\section{Additional Preliminary Definitions and Lemmata}\label{sec:defsandlems}



\begin{definition}[Coin Tossing]\label{def:coin}
An \emph{ideal coin tossing} is a functionality denoted with $\F^{\coin}$ that interacts with two parties \A and \B, samples a uniform string $r\in\bits^*$ and sends $r$ to $\A$ and $\B$.
\end{definition}

\newcommand{\extract}{\ensuremath{\mathsf{ext}}\xspace}

\begin{definition}[Extractable Commitments]\label{def:com}
An \emph{extractable commitment scheme} consists of three algorithms.
\begin{description}
\item[$\com(x,r)$:] Commits to $x$ using randomness $r$. 
\item[$\open(\com,x,r)$:] Outputs $1$ if commitment $\com\in\com(x,r)$.
\item[$\extract(\com,\aux)$:] Given some auxiliary information, it extracts committed value $x$. 
\end{description}
For security, we ask that it is hiding, i.e. for any $x,m$, $x, \com(x,r)$ is indistinguishable from $m,\com(x,r)$ and that it is binding, i.e. for any $x$, $\extract(\com(x,r))$ outputs $x$.
\end{definition}

An extractable commitment can easily constructed using a random oracle by defining $\com(x,r):=H(x,r)$, $\open$ simply evaluates $\H$ and checks equality and the $\extract$ algorithm observes the random oracle queries from which $x$ can be learned.

\subsection{Key Agreement}\label{sec:addKA}
We give the following additional security definition for key agreement protocols.

\begin{definition}[One-Round Uniform Key Agreement]
We call a \UKA \emph{one-round uniform key agreement} if the function $\mes_{\B}\leftarrow\B(\tape_{\B},\mes_\A)$ does not depend on $\mes_A$ and can be computed solely using input $\tape_{\B}$. More precisely, there is a function $\B'$ such that for any $\mes_{\A}$, $\B'(\tape_{\B})=\B(\tape_{\B},\mes_{\A})$, which we will in the following refer to with $\B$ as well. 
\end{definition}

\begin{definition}[Multi-Instance Uniformity]
We call a \UKA $Q$ \emph{multi-instance uniform} if for any ppt distinguisher \D,
$$
|\Pr[\D^{\O_{\A}}(1^{\sec})]=1]-Pr[\D^{\O_{u}}(1^{\sec})=1]|=\negl,
$$
where $\O_{\A}$ outputs $\mes_\A\leftarrow\A(\tape_\A)$ for fresh randomness $\tape_\A$ and $\O_u$ outputs $u\leftarrow\G$ and $Q$ is a bound on the amount of queries to $\O_{u}$, $\O_{\A}$.
\end{definition}



\begin{definition}[Multi-Instance Key Indistinguishability]
We call a \UKA $(Q,n)$ \emph{multi-instance key indistinguishable} if for any ppt distinguisher \D,
$$
|\Pr[\D^{\O_{\langle \A,\B\rangle}, \O_{\key}}(1^{\sec})]=1]-Pr[\D^{\O_{\langle \A,\B\rangle},\O_{u}}(1^{\sec})=1]|=\negl,
$$
where $\O_{\langle \A,\B\rangle}$ outputs on the $i$-th query a transcript $\T_i:=\langle \A_i,\B_i\rangle$, $\O_{\key}$ outputs on query $j$, key $\key_j=\EK(\tape_{\A,j},\mes_{\B,j})=\EK(\tape_{\B,j},\mes_{\A,j})$ that matches transcript $\T_i$. $\O_u$ outputs a uniform element $u$ from the key domain. $\O_{\langle \A,\B\rangle}$ uses fresh random tapes $\tape_{\A,i},\tape_{\B,i}\leftarrow\bits^*$ for every query. $Q$ is a bound on the amount of queries to $\O_{\langle \A,\B\rangle}$, where $n$ bounds the amount of queries to $\O_{\key}$, $\O_{u}$. 
\end{definition}

In case of a one-round \UKA, we define a stronger version of the multi-instance key indistinguishability, which we call one-round multi-instance key indistinguishability.

\begin{definition}[One Round Multi-Instance Key Indistinguishability]
We call a one-round \UKA $(Q,n)$ \emph{one-round multi-instance key indistinguishability} if for any ppt distinguisher \D,
$$
|\Pr[\D^{\O_{\A}, \O_{\key}}(1^{\sec},\mes_\B)]=1]-Pr[\D^{\O_{\A},\O_{u}}(1^{\sec},\mes_\B)=1]|=\negl,
$$
where $\mes_{\B}\leftarrow\B(\tape_{\B})$ for uniform $\tape_{\B}$. $\O_{\A}$ outputs on the $i$-th query $\mes_{\A,i}\leftarrow \A(\tape_{\A,i})$ for uniform $\tape_{\A,i}$. $\O_{\key}$ outputs on query $j$, key $\key_j=\EK(\tape_{\A,j},\mes_{\B})=\EK(\tape_{\B},\mes_{\A})$. $\O_u$ outputs a uniform element $u$ from the key domain. $Q$ is a bound on the amount of queries to $\O_{\A}$, where $n$ bounds the amount of queries to $\O_{\key}$, $\O_{u}$. 
\end{definition}

In the next lemmata, we show that all the security notions are implied by the standard definitions, but potentially with a polynomial security loss.
 
\begin{lemma}\label{lem:multuniform}
Let \UKA be uniform except probability $\epsilon$, then it is $Q$ multi-instance uniform except at most probability $Q\epsilon$.
\end{lemma}
\begin{proof}
This follows straightforwardly from using a simple hybrid argument. Hybrid $\hyb_{i}$ samples $\mes_{\A,j}$ for $j\leq i$ from $\O_u$ and for $j>i$ from $\O_{\A}$. If there is an adversary that distinguishes $\hyb_i$ from $\hyb_{i+1}$ for any $i$, then we can break the uniformity of \UKA by distinguishing $\mes_{\A,i+1}$ from uniform.  
\pe
\end{proof}

\begin{lemma}\label{lem:keytomultkey}
Let \UKA be key indistinguishable except probability $\epsilon$, then it is $(Q,n)$ multi-instance key indistinguishable except at most probability $Q\epsilon$. 
\end{lemma}

\begin{proof}
Again, we use a hybrid argument over hybrids $\hyb_i$. In $\hyb_i$, $(\mes_{\A,j},\mes_{\B,j}),\key_j$ is sampled from $\O_{\langle \A,\B\rangle}\times\O_u$ for $j\leq i$ and from $\O_{\langle \A,\B\rangle}\times\O_\key$ for $j>i$. If one distinguishes $\hyb_i$ from $\hyb_{i+1}$ for some $i$, one breaks the key indistinguishability. 
\pe
\end{proof}

\begin{lemma}\label{lem:oneroundkeytomultkey}
Let a one-round \UKA be key indistinguishable except probability $\epsilon$, then it is $(Q,n)$ one-round multi-instance key indistinguishable except at most probability $Q\epsilon$. 
\end{lemma}

\begin{proof}
This lemma follows for the same reason as \lemmaref{lem:keytomultkey}.
\pe
\end{proof}


\subsection{Oblivious Transfer}\label{sec:addOT}


\begin{lemma}[Repeat of \lemmaref{lemma:is_a}]\label{lemma:is_a_repeat}
	Let the distribution of OT strings be efficiently sampleable. 
	Then $\OOT^\U$-security implies $\OOT^{\send}$ as well as $\OOT^\rec$-security. $\OOT^{\send}$ or $\OOT^\rec$-security imply $\OOT^\E$-security.
\end{lemma}
\input{proofs/is_a.tex}

In the following, we give a generalized definition of OT.

\begin{definition}[Generalize Ideal $k$-out-of-$n$ Oblivious Transfer]\label{def:got}
	A (generalized) \emph{ideal $k$-out-of-$n$ oblivious transfer} is a functionality that interacts with two parties, a sender \send and a receiver \rec. Let $\set\subseteq[n]$ of size $k$ and  $s_1,...,s_n\in \{0,1\}^\ell$.
	
	The functionality is publicly parameterized by one of the following message sampling methods:
	\begin{description}
		\item[] \textsc{Sender Chosen Message:} $\send$ sends the circuit $\mathcal{M} : [n] \rightarrow \{0,1\}^\ell$ to the functionality which defines $s_i:=\mathcal{M}(i)$.
		
		\item[] \textsc{Receiver Chosen Message:} \rec sends the circuit  $\mathcal{M} : [k] \rightarrow \{0,1\}^\ell$ to the functionality which defines $s_{\set_i}:=\mathcal{M}(i)$ for $i\in[k]$ and uniformly samples $s_i\gets\{0,1\}^\ell$ for $i\in\set\setminus[n]$.
		
		\item[] \textsc{Uniform Message:} The functionality uniformly samples $s_i\gets\{0,1\}^{\ell}$ for $i\in[n]$. 
		
		\item[] \textsc{Endemic:} If $\send$ is corrupt, then $\send$ sends the circuit $\mathcal{M} : [n] \rightarrow \{0,1\}^\ell$ to the functionality which defines $s_i:=\mathcal{M}(i)$.
		
		If \rec is corrupt, \rec sends the circuit  $\mathcal{M} : [k] \rightarrow \{0,1\}^\ell$ to the functionality which defines $s_{\set_i}:=\mathcal{M}(i)$ for $i\in[k]$.
		
		All remaining $s_i$ for $i\in [n]$ are uniformly samples $s_i\gets\{0,1\}^\ell$.
	\end{description}
	
	The functionality is publicly parameterized by one of the following selection methods:
	\begin{description}
		\item[] \textsc{Receiver Selection:} \rec sends the circuit $\mathcal{S}:[n]\rightarrow\{0,1\}$ to the functionality where the support of $\mathcal{S}$ is of size $k$. The functionality defines $\set:=\{i \mid \mathcal{S}(i)=1\}$.
		\item[] \textsc{Uniform Selection:} The functionality uniformly samples $\set\gets\mathbb{P}([n])$ s.t. $|\set|=k$.
	\end{description}
	
	As specified by the message sampling method, the oracle receives the circuit $\mathcal{M}$ from the appropriate party if one is called for.  As specified by the selection method, the functionality receives the circuit $\mathcal{S}$ if one is called for. 
	Thereafter, upon receiving the message $(\textsc{Output}, i)$ from \send, respond with $s_i$. Upon receiving $(\textsc{Output}, i)$ from \rec and if $i\in \set$,  respond with $s_i$. 
	
	We denote the ideal functionalities for sender chosen, receiver chosen, uniform and endemic with receiver selection as $\OOT^\send, \OOT^\rec,\OOT^\U,\OOT^\E$, respectively. The analogous oracles for Uniform Selection are denoted as  $\OOT^{\send u},$ $\OOT^{\rec u}, \OOT^{\U u}, \OOT^{\E u}$, respectively.
\end{definition}
\begin{remark}
	When $n$ is polynomial in the security parameter $\kappa$, we simplify the above definition to \definitionref{def:ot} to allow the parties directly input the appropriate $s_i$ messages as opposed to specifying a circuit $\mathcal{M}$. Similarly for the set $\set:=\{i \mid \mathcal{S}(i)=1\}$. Lastly, instead of querying the oracle with $(\textsc{Output}, i)$, the oracle sends $(s_i)_{i\in [n]}$ to \send and $(\set, (s_i)_{i\in\set})$ to \rec. This simplification can trivially be simulated when $n=\textsf{poly}(\kappa)$.
\end{remark}


The following transformation allows to transform an OT where the receiver's choice bit is chosen to an OT with a random choice bit. This transformation is very useful in the context of OT extension.

\begin{figure}
\centering
\framebox{
\begin{tikzpicture}
\node [anchor=west] at (0,5) {Sender:};
\node [anchor=west] at (7.5,5) {Receiver:};
\draw [thick] (4.75,4.65)--(5.75,4.65)--(5.75,3.65)--(4.75,3.65)--cycle;
\node at (5.25,4.125){$\OOT^\send$};
\node [anchor=west] at (7.5,4.5){$\set'\gets \mathbb{P}([n])$ s.t. $|\set'|=k$};
\draw [thick, <-] (5.75,4.5)-- node [midway,above]{$\set'$}(7.25,4.5);
\draw [thick, ->] (5.75,3.85)-- node [midway,above]{$(s_{\pi(i)})_{i\in \set'}$}(7.25,3.85);
\node [anchor=west] at (0,4.5) {$\pi\leftarrow\Pi([n])$};
\draw [thick, ->] (3.25,3)-- node [midway, above]{$\pi$} (7.25,3);
\draw [thick, ->] (3.25,4.5)-- node [midway,above]{$(s_{\pi(i)})_{i\in [n]}$}(4.75,4.5);
\node [anchor=west] at (0,2.5) {output $(s_{i})_{i\in[n]}$};
\node [anchor=west] at (7.5,3) {$\set:=\{j \mid \exists i, j=\pi(i)\}$};
\node [anchor=west] at (7.5,2.5) {output $\set, (s_i)_{i\in\set}$};
\end{tikzpicture}
}
% 	\framebox{\begin{minipage}{0.95\linewidth}
% 			Input: The sender \send and receiver \rec have no input.
% 			\begin{enumerate}
% 				\item \label{step:uniformSelect_step1} \rec uniformly samples $\set'\gets \mathbb{P}([n])$ s.t. $|\set'|=k$. \rec sends $\set'$ to $\OOT^{\E}$ and receives $(s_i')_{i\in \set'}$ in response. \send receives $(s_i')_{i\in [n]}$. 
% 				\item \label{step:uniformSelect_step2} \send samples a random permutation $\pi : [n] \rightarrow [n]$ and sends it to \rec.
% 				\item \label{step:uniformSelect_step3} \send outputs $(s_i)_{i\in [n]}$ and \rec outputs $(\set, (s_i)_{i\in\set})$ where $s_i:=s_{\pi(i)}'$ and $\set:=\{j \mid \exists i, j=\pi(i)\}$.
% 			\end{enumerate}
% 	\end{minipage}}
	\caption{Uniform selection $k$-out-of-$n$ OT protocol $\Pi^{\send u}$ in the $\OOT^{\send}$ hybrid. $\Pi([n])$ is the set of permutations over $[n]$.}
	\label{fig:uniformSelect}
\end{figure}



\begin{lemma}
	$\Pi^{\send u}$ of \figureref{fig:uniformSelect} realizes the  ideal uniform selection sender chosen message OT $\OOT^{\send u}$ (\definitionref{def:ot}) with unconditional security in the $\OOT^{\send}$ hybrid.
\end{lemma}

\begin{remark}
	The same transformation applies to $\OOT^\U,\OOT^\E, \OOT^\rec$ except \send does not input anything to $\OOT^*$.
\end{remark}
 

\begin{proof}[sketch]
	Consider a corrupt \send. Due to $\set'$ being uniformly distributed, so is $\set=\pi(\set')$ since $\pi$ is one to one. Consider a corrupt \rec. The simulator receives $\set'$ from \rec and the $\set,(s_i)_{i\in\set}$ from $\OOT^{\send u}$. The simulator uniformly samples $\pi$ s.t. $\{s_i\}_{i\in\set} =\{s_{\pi(i)}\}_{i\in\set'}$ and completes the protocol.
	\pe
\end{proof}


\subsection{Diffie-Hellman Key Exchange}\label{sec:DDH}
In \figureref{fig:DH}, we depict the Diffie-Hellman key exchange. 
\input{figures/DH.tex}
It can be proven secure under the decisional Diffie-Hellman (DDH) assumption.
\begin{definition}[Decisional Diffie-Hellman (DDH) Assumption]
For a group $\G$, the \emph{decisional Diffie-Hellman} assumption is hard if for any ppt distinguisher \D,
$$
|\Pr\lb \D(1^\sec,\lb 1\rb,\lb a\rb,\lb b\rb,\lb ab\rb)=1\rb-\Pr\lb D(1^\sec,g,\lb a\rb,\lb b\rb,\lb c\rb)=1\rb|=\negl,
$$
where $a\leftarrow\Z_p$, $b\leftarrow\Z_p$ and $c\leftarrow\Z_p$.
\end{definition}

The following lemma states that multi-instance DDH is secure under the DDH assumption with a security loss equal to the amount of instances.

\begin{lemma}\label{lem:DHuniform}
Let DDH be secure over \G except advantage $\epsilon$, then $n$ multi-instance DDH is secure over \G except at most advantage $n\epsilon$.
\end{lemma}

\begin{proof}
This lemma follows from a simple hybrid argument. We define hybrid $\hyb_i$ as the distribution over $\lb \vec{a}\rb,\lb b\rb,\lb \vec{c}\rb$, where for all $j\leq i$, $c_j=a_jb$ and for $j>i$, $c_j\leftarrow\Z_p$. If $\D$ distinguishes hybrid $\hyb_i$ from $\hyb_{i+1}$, it breaks the DDH assumption over \G.
\pe
\end{proof}

