\section{Optimality of the Result}

\newcommand{\OG}{\ensuremath{\O_{\mathsf{G}}}\xspace}
\newcommand{\OK}{\ensuremath{\O_{\mathsf{K}}}\xspace}
\newcommand{\sk}{\ensuremath{\mathsf{sk}}\xspace}
\newcommand{\pk}{\ensuremath{\mathsf{pk}}\xspace}
\renewcommand{\L}{\ensuremath{\mathsf{L}}\xspace}
\newcommand{\LOG}{\ensuremath{\L_{\OG}}\xspace}
\newcommand{\LOK}{\ensuremath{\L_{\OK}}\xspace}
\newcommand{\E}{\ensuremath{\mathsf{E}}\xspace}



\begin{definition}[Asymmetric Random Oracle]
An \emph{asymmetric random oracle} consists of two oracles \OG and \OK, with the following description.
\begin{description}
\item[\OG:] \OG has a list \LOG that is empty in the beginning. On an (empty) query, \OG samples $\sk\leftarrow\bits^{\sec}$. If $(\sk,*)\not\in\LOG$, it samples  $\pk\leftarrow\bits^{\sec}$. Then it outputs and stores  $(\sk,\pk)$ in \LOG. If $(\sk,*)\in\LOG$, \OG outputs entry $(\sk,\pk)$ of \LOG.
\item[\OK:] \OK has a list \LOK, which is empty in the beginning, and access to list \LOG. On a query $(\sk_1,\pk_2)$, \OK looks up $\pk_1$ s.t. $(\sk_1,\pk_1)\in\LOG$. If $(\pk_1,\pk_2,\key)$ or $(\pk_2,\pk_1,\key)$ are in \LOK, it outputs $\key$. Otherwise it samples $\key\leftarrow\bits^{\sec}$, outputs $\key$ and stores $(\pk_1,\pk_2,\key)$ in \LOK.  
\end{description} 
\end{definition}

\begin{lemma}
Let $\langle \A, \B\rangle$ be a protocol between two parties \A and \B with access to a random oracle \H and an asymmetric random oracle $(\OG, \OK)$, where the outputs of \OK are submitted to \A, \B after all messages are sent. Then, there is an algorithm \E that takes as input the transcript $\langle \A, \B\rangle$ and outputs two lists $\L_1, \L_2$, such that with high probability, the views of \A and \B are mutually independent conditioned on $\L_1$, $\L_2$, transcript $\langle \A, \B\rangle$ and $(\pk_{\A,i},\pk_{\B,j},\key)_{i\in[Q_{\A}],j\in[Q_{\B}]}\subseteq\LOK$.
\end{lemma}

\begin{lemma}
Let $\langle \A, \B\rangle$ be a protocol between two parties \A and \B with access to a random oracle \H and an asymmetric random oracle $(\OG, \OK)$, where \A makes $Q_{\A}$ and \B $Q_{\B}$ queries to $\OG$. Then, there is an algorithm \E that takes as input the transcript $\langle \A, \B\rangle$, the $Q_{\A}\cdot Q_{\B}$ asymmetric intersection queries $(\pk_{\A,i},\pk_{\B,j},\key)_{i\in[Q_{\A}],j\in[Q_{\B}]}\subseteq\LOK$ and outputs two lists $\L_1, \L_2$, such that with high probability, the views of \A and \B are mutually independent conditioned on $\L_1$, $\L_2$, transcript $\langle \A, \B\rangle$ and $(\pk_{\A,i},\pk_{\B,j},\key)_{i\in[Q_{\A}],j\in[Q_{\B}]}\subseteq\LOK$.
\end{lemma}



\begin{theorem}
There is no secure $k$ out of $n$ endemic OT where the sender makes at most $n$ queries to $\OK$ and the receiver makes at most $k-1$ queries to $\OG$. 
\end{theorem}

\begin{proof}
We show that there is either a sucessful malicious sender or receiver that breaks the protocol. We start by constructing a malicious sender that receives $k-1$ OT strings learned by the receiver and tries to determine the $k$-th OT string. An attack that is successful with more than probability $\frac{1}{n-k-1}$ would violate the security of the OT. 

On a high level, the malicious sender chooses the following strategy. It runs the normal protocol interacting with \rec to receive the OT strings $(s_i)_{i\in[n]}$. Further, \rec sends him $k-1$ of his learned strings $(s_i)_{i\in\set_1}$, where $\set_1$ has size $k-1$. It will then run algorithm \E to learn the two lists $\L_1$, $\L_2$, where it provides \E his own list of query answer pairs of $\OK$, which contains all asymmetric intersection queries. 

Now, given the transcript, $L_1$, $L_2$ the views of the malicious sender and \rec are mutually independent. This allows the malicious sender to resample the view of \rec such that its output, $(s_{\rec,i})_{i\in\set_{\rec}}$, where $\set_{\rec}$ has size $k$, is still consistent with its own view, i.e. $(s_{\rec,i})_{i\in\set_{\rec}}\subset(s_i)_{i\in[n]}$. The malicious sender uses this resampling procedure to determine 
\end{proof}