\newcommand{\msng}{\textcolor{red}{(Missing References?)}}

\section{Introduction}

An oblivious transfer (OT) \cite{Rabin81,C:EveGolLem82} is a cryptographic primitive often used in the context of secure multi party computation, which allows to preserve the privacy during a joint computation. Among others, it solves the task of securely distributing cryptographic keys for garbled circuits, which can be seen as encrypted programs. The combination of garbled circuits and oblivious transfer gives a generic solution for securely computing any functionality between two parties \cite{FOCS:Yao82b,FOCS:Yao86,STOC:Kilian88,C:IshPraSah08} and multiple parties \cite{C:CreVanTap95,EC:BenLin18,EC:GarSri18a}. \msng  

In an OT, a sender and a receiver interact in a protocol and at the end of the protocol, the sender outputs two strings $s_0$, $s_1$ while the receiver outputs $b, s_b$ for choice bit $b$. Security asks that the sender does not learn $b$ and the receiver does not learn $s_{1-b}$. It is known that an OT implies key exchange and can be constructed from special types of public key encryption \cite{FOCS:GKMRV00,C:PeiVaiWat08,cryptoeprint:2018:473} or certified trapdoor permutations \cite{C:OstRicSca15}. Though, all of these solutions come with a drawback when it comes to practical deployment. The OT construction of Gertner et al. \cite{FOCS:GKMRV00} only achieves a weak security notion that requires that both, sender and receiver follow the protocol description. The works of Ostrovksy et al. \cite{C:OstRicSca15} and Friolo et al. \cite{cryptoeprint:2018:473} require four rounds and a special type of commitment protocol \cite{STOC:Kilian92,C:OstRicSca15} that does not have an efficient instantiation so far. Peikert et al. \cite{C:PeiVaiWat08} require a very specific type of public key encryption (PKE) that they call dual-mode cryptosystem, which is less efficient than standard PKE and implied by DDH, QR and LWE with weaker parameter choices\footnote{Peikert et al. require SIVP hardness for approximation factor $\tilde{O}(n^{3.5})$ while Regev's PKE \cite{STOC:Regev05} only requires $\tilde{O}(n^{1.5})$.} but not known from many other assumptions like CDH or LPN. Naor and Pinkas \cite{SODA:NaoPin01} constructed OTs from the DDH with a random oracle and Brakerski and D\"ottling \cite{TCC:BraDot18} from the LWE assumption that requires similar parameter choices as Peikert et al \cite{C:PeiVaiWat08}.

In practice, a common approach is to realize a critical amount of OTs in the random oracle model (ROM) \cite{CCS:BelRog93,SODA:NaoPin01} and then extend the amount of OTs to the desired amount of OT using OT extension \cite{STOC:Beaver96a,C:IKNP03,RSA:OrrOrsSch17,EC:ALSZ15,C:KelOrsSch15}. A random oracle is an ideal hash function that usually is instantiated with a concrete hash function in the implementation. The ROM brings major efficiency improvements and is therefore very common for practical cryptographic constructions. Though, it seems to come at a cost of security guarantees, more precisely there exist specifically crafted schemes that are secure in the ROM but insecure when replacing the random oracle with any hash function \cite{STOC:CanGolHal98}. Nevertheless, it seems to be very unlikely that this shortcoming of the ROM can be exploited to break protocols that are not crafted towards a break. 

In the ROM, Bellare \& Micali \cite{C:BelMic89} constructed OT based on the CDH assumption. Chou \& Orlandi \cite{LC:ChoOrl15} claimed a more efficient OT construction which was proven with some caveats under the GapDH assumption \cite{cryptoeprint:2017:1011}. Hauck \& Loss improved the construction to base it on the CDH assumption \cite{cryptoeprint:2017:1011}. \textcolor{red}{maybe explain more why this is meaningful}

A drawback of the more efficient constructions of Chou \& Orlandi, and Hauck \& Loss is that they require three rounds. The former also suffers technical issues with the ability to extract the input of the receiver \cite{LC:ChoOrl15}. Further, unlike than the more generic constructions based on PKE, they are tailored to specific assumptions. A more generic construction for OT in the ROM would be preferable since it allows an easier transition to different assumption like LWE or LPN, which unlike CDH and DDH are assumed to offer security in presence of quantum computers. We therefore focus on the question:

\begin{center}
\emph{How to construct a highly efficient and fully secure OT in the ROM?}
\end{center}

For efficiency, we ask for a minimal round complexity, low computational complexity and compatibility with OT extension techniques.

\subsection{Our Contribution}

We revisit the security definition of maliciously secure oblivious transfer. We observe that there is very basic security definition which has not been considered in previous literature. We call this security \emph{endemic} security and denote an OT that is endemically secure with endemic OT. 

While the new security defintion might seem unnatural at the first glance, it turns out to be very important to achieve a minimal round complexity as well as to analyze the security of optimized existing OT and OT extension protocols.

In \sectionref{sec:relot}, we compare our new security notion with previous notions and show that an endemic OT can efficiently  be tranformed such that classical security notions are achieved but potentially at the cost of a higher round complexity. We also show that classical security notions do not permit a one round OT.

Given this novel security definition, we give in \sectionref{sec:endemicOT} a construction in the ROM that transforms any two message key agreement protocol, where the distribution of one of the messages is computationally close to uniform, into an endemically secure two message $1$-out-of-$n$ oblivious transfer\footnote{In \namedref{Appendix}{sec:allbutone}, we show how the framework can be adapted to obtain an endemically secure $(n-1)$-out-of-$n$ OT.}. Further, 
if the key agreement protocol is a one round protocol, we obtain a one round endemic OT. This implies that we get a one round endemic OT from DDH, CDH and two round endemic OT from LWE, LPN, McEliece and Subset Sum.

In \sectionref{sec:inst}, we show how to efficiently instantiate our construction based on the Diffie-Hellman key exchange and the Module LWE (\MLWE) based Kyber key encapsulation \cite{NISTPQC-R1:CRYSTALS-KYBER17}. We emphasize that it can also be instantiated with many of the other NIST post-quantum standardisation candidates and is to the best of our knowledge the first implementation of a quantum resistant OT. We provide details of their implementation and their performance in \sectionref{sec:impl}.

In \sectionref{sec:otext}, we show that our construction is compatible with OT extension techniques. Concretely, we show that endemic OTs can be extended to a larger amount of endemic OTs using only one additional round. This allows us to obtain $\mathsf{poly}(\sec)$ OTs using only $O(\sec)$ public key operations in only two rounds. We revisit the OT extension protocol of Keller et al. and Orr{\`u} et al. \cite{C:KelOrsSch15,RSA:OrrOrsSch17} under endemic security. It turns out that its uniform message security can be fully broken. We point out attacks and provide fixes such that classical, uniform and endemic security can be obtained. Finally, we observe that most OT extension protocols are implemented using an ideal cipher in place of a random oracle. However, these implementations have no security proofs and we show that they too can be fully broken. We give new protocols and proofs in the ideal cipher model which allows a 10 times speed up when implemented. 

\input{techoverview.tex}
