
\newif\iffullversion

\fullversionfalse

\iffullversion    
	\documentclass[11pt]{article}
	\usepackage[margin=1in]{geometry}
	\usepackage{authblk}
\else
	%\documentclass[runningheads]{llncs}
	%\pagestyle{plain}
	\documentclass[sigconf]{acmart}	
\fi

%\usepackage[a4paper, total={6in, 9in}]{geometry}

\input{header.tex}
 
 %proof symbol
 %\iffullversion    
	\newcommand{\pe}{}
%\else
%	\newcommand{\pe}{\qed}
%\fi

\title{Endemic Oblivious Transfer}
 
 %
 \iffullversion   
 \date{}
 \author{Daniel Masny}
 \author{Peter Rindal}
 \affil{VISA Research}
 \else
 \author{Daniel Masny and Peter Rindal}
 \affiliation{VISA Research}
%   \author{Peter Rindal}
%  \affiliation{VISA Research}
 \fi
\begin{document}

\iffullversion 
\maketitle
\fi
\begin{abstract}
Oblivious Transfer has played a crucial role in the design of secure multi party computation. Nevertheless, there are not many practical solutions that achieve simulation based security and at the same time instantiable based on different assumptions.

In this work, we consider a simulation based security notion that we call endemic security. We show how to construct highly efficient oblivious transfer in the random oracle model that achieves endemic security under a wide range of assumptions, among them DDH, CDH, LWE and coding based assumptions. We construct a secure oblivious transfer based on DDH that takes only a single communication round which allows significant performance gains. We also instantiate our oblivious transfer with the Crystals.Kyber key agreement. Our implementation shows that both instantiations can be computed in under one millisecond. 

Further, we revisit, correct and improve existing oblivious transfer extension techniques. We provide an implementation of an oblivious transfer extension protocol in the ideal cipher model that is actively secure, processing up to 23 million OTs per second and up to $10$ times faster than previous secure implementations. We also show that our framework can compute endemically secure OT extension and the base OTs in just two rounds.

\end{abstract}

\iffullversion 
\else
\copyrightyear{2019} 
\acmYear{2019} 
\acmConference[CCS '19]{2019 ACM SIGSAC Conference on Computer and Communications Security}{November 11--15, 2019}{London, United Kingdom}
\acmBooktitle{2019 ACM SIGSAC Conference on Computer and Communications Security (CCS '19), November 11--15, 2019, London, United Kingdom}
\acmPrice{15.00}
\acmDOI{10.1145/3319535.3354210}
\acmISBN{978-1-4503-6747-9/19/11}

\maketitle
\fi

\input{temp.tex}
\input{intro.tex}
\input{prelim.tex}
\input{relOT.tex}
\input{orimp.tex}
\input{KAtoOT.tex}

\input{otExt.tex}

%\input{imp.tex} 
\input{implementation.tex}


\bibliographystyle{alpha}
\bibliography{bib,cryptobib/abbrev3,cryptobib/crypto}

\iffullversion 
\appendix
\input{defandlemmas.tex}
\input{roundcomp.tex}
\input{allbutoneOT.tex}
\input{instatiation.tex}
%\input{instantiationsAppendix.tex}
\input{otExtAppendix.tex}
\else
\appendix
\input{otExtAppendix.tex}
%\input{instatiation.tex}
\fi

%\input{otExtAppendix.txt}
\end{document}