
\section{OT Extension }\label{sec:extApp}


\iffullversion
\else

\subsection{Protocol Diagrams}
\input{figures/extDiagrams.tex}



\subsection{Proof of \lemmaref{lem:malRec} (Attack of $\Pi^\textsf{OOS}$)}
\input{proofs/attack_BadT0.tex}


\subsection{Proof of \lemmaref{lem:malRec2} (Attack of $\Pi^\textsf{OOS+}$)}
\input{proofs/attack_Selection.tex}


\subsection{Proof of \lemmaref{lem:malSend} (Attack of $\Pi^\textsf{OOS+}$)}
\input{proofs/attack_AllOnes.tex}

\subsection{Proof of \lemmaref{lem:ext_R_S}: $\OOT^\U$ Extension with a Random Oracle}
\input{proofs/ext_S_U.tex}


\subsection{Proof of \lemmaref{lem:ext_R_S}: $\OOT^\send$ Extension with an Ideal Cipher}



%We begin with the $\Pi^{\textsf{ext-R}}$ protocol defined in \definitionref{def:ext_R_S}.
\begin{definition}\label{def:ext_R_S}
	Let $\Pi^{\textsf{ext-S}\pi}$ be the protocol of \figureref{fig:otExt} where $\OOT:=\OOT^\rec$ and the random oracle $\H(i,x)$ required by $\Pi^{\textsf{ext-E}}$ is replaced as follows: after \stepref{step:consistency}, \send samples $k\gets\{0,1\}^{\kappa}$ and sends it to \rec. Both parties define $\H(x)=\pi_k(x)+x$ where $\pi:\{0,1\}^{\kappa} \times \mathbb{F}^\nc_2 \rightarrow\{0,1\}^\kappa$ is an ideal cipher. Note: the $i$ parameter of $\H$ is removed.
\end{definition}
\begin{lemma}\label{lem:ext_R_S}
	The $\Pi^{\textsf{ext-S}\pi}$ protocol realizes 1-out-of-$N$ $\OOT^\send$-security, for $N=\textsf{poly}(\kappa)$. Against a malicious \rec,  $\Pi^{\textsf{ext-R}\pi}$ realizes $\OOT^\U$-security. That is, the input messages of an honest \send are sampled uniformly from $\{0,1\}^\kappa$ by the protocol.
\end{lemma}

\input{proofs/ext_R_S.tex}

\begin{definition}\label{def:ext_U_U}
	Let $\Pi^{\textsf{ext-U}\pi}$ be the protocol of \figureref{fig:otExt} where $\OOT:=\OOT^{\U u}$ and the random oracle $\H(i,x)$ required by \figureref{fig:otExt} is replaced as follows:
	\begin{enumerate}
		\item In round one, \send samples $k\gets\{0,1\}^{\kappa}$ and sends a commitment of $k$ to \rec.
		\item After \stepref{step:consistency}, \send decommits $k$ to \rec who aborts if it fails.
		\item Both parties define $\H(x)=\pi_k(x)+x$ where $\pi:\{0,1\}^{\kappa} \times \mathbb{F}^\nc_2 \rightarrow\{0,1\}^\kappa$ is an ideal cipher. Note: the $i$ parameter of $\H$ is removed.
	\end{enumerate}
\end{definition}

\subsection{Proof of \lemmaref{def:ext_U_U}:  $\OOT^\U$ Extension with an Ideal Cipher}
\begin{lemma}\label{lem:ext_U_U}
	The $\Pi^{\textsf{ext-U}\pi}$ protocol realizes 1-out-of-$N$ $\OOT^\U$-security, for $N=\textsf{poly}(\kappa)$.
\end{lemma}
\input{proofs/ext_U_U.tex}




\subsection{ $\OOT^\rec$ Extension with an Ideal Cipher}

\begin{definition}\label{def:ext_S_R}
	Let $\Pi^{\textsf{ext-\rec}\pi}$ be the protocol of \figureref{fig:otExt} where $\OOT:=\OOT^{\U u}$ and the random oracle $\H(i,x)$ required by $\Pi^{\textsf{ext-E}}$ is replaced as follows: $\H(x)=\pi(x)+x$ where $\pi: \mathbb{F}^\nc_2 \rightarrow\{0,1\}^\kappa$ is an ideal permutation. Note: the $i$ parameter of $\H$ is removed.
\end{definition}
\begin{lemma}\label{lem:ext_S_R}
	The $\Pi^{\textsf{ext-\rec}\pi}$ protocol realizes 1-out-of-$N$ $\OOT^\rec$-security, for $N=\textsf{poly}(\kappa)$.
\end{lemma}
\begin{proof}[sketch]
	The proof follows the same strategy as \lemmaref{proof:ext_U_U} except $\pi$ is not keyed. As such, \rec can compute $\H(\tt_i)$ \emph{before} making their selection $x_i$. This can be simulator by having the simulator extract $\H(\tt_i)$ as their chosen message. 
\end{proof}

\fi